A Study of Common Bug Fix Patterns in Rust \thanks{Competing Interests: We have no competing interests and are funded by a Discovery Grant from Canada's Natural Science and Engineering Research Council.}

### 2022-12-03 methodology.tex
wrapping up
final commit before submission

Syn\footnote{\url{https://crates.io/crates/syn}} is a Rust crate built for the Rust procedural macro implementation. However, it includes a parser which is suitable for our purposes; we simply had to write a preprocessor to transform Syn AST output into Python dictionaries. Syn handles all of Rust. Each of our datapoints specifies whether any Syn non terminal (\texttt{NT}) is present or absent, i.e. containing one dimension per non terminal. However, we are also interested in change patterns that involve the borrow checker (BC), so we also add a dimension reflecting the presence of a set of BC-related elements (\texttt{BCE}) that we identified, e.g. \texttt{clone}, \texttt{Rc}, \texttt{Box}. The full list of \texttt{BCE} elements can be found in our replication package.

@@

Now that we have set up our code analysis pipeline, we can start mining the Rust repositories. We target the top 18 most-starred Rust projects on GitHub, at the time of data collection. Table~\ref{table:repos} summarizes our benchmarks. Because we are interested in changes, we computed (using process metrics provided by our mining library) the average code churn of the files within the projects. denoland/deno and swc-project/swc are the projects with largest number of LOCs and highest average code churn, respectively. Unsurprisingly, we captured a lot of instances from these two projects in our final clusters.

>>>>

Syn\footnote{\url{https://crates.io/crates/syn}} is a Rust crate built for the Rust procedural macro implementation. However, it includes a parser which is suitable for our purposes; we simply had to write a preprocessor to transform Syn AST output into Python dictionaries. Syn handles all of Rust. Each of our datapoints specifies whether any Syn non terminal (\texttt{NT}) is present or absent, i.e. containing one dimension per non terminal. However, we are also interested in change patterns that involve the borrow checker (BC), so we also add a dimension reflecting the presence of a set of BC-related elements (\texttt{BCE}) that we identified, e.g. \texttt{clone}, \texttt{Rc}, \texttt{Box}. The full list of \texttt{BCE} elements can be found in our replication package\footnote{\url{https://zenodo.org/record/7388618}}.

@@

Now that we have set up our code analysis pipeline, we can start mining the Rust repositories. We target the top 18 most-starred Rust projects on GitHub, at the time of data collection. Table~\ref{table:repos} summarizes our benchmarks. Because we are interested in changes, we computed (using process metrics provided by our mining library) the average code churn of the files within the projects. swc-project/swc, nushell/nushell, and denoland/deno are the projects with largest number of LOCs. Unsurprisingly, we captured a lot of instances from these projects in our final clusters.
